\documentclass[a4paper,12pt]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}

\title{LCC Analysis of a Crushing Plant}
\author{Lule\aa{} University of Technology - Division of Operation and Maintenance}
\date{\today}

\begin{document}

\maketitle

\section{Background}
In this assignment, you are required to perform a \textbf{Life Cycle Cost (LCC) analysis} of a \textbf{crushing plant}. The plant consists of a \textbf{crusher unit, a conveyor, and a screen} adapted for the desired grain size. You are responsible for this production facility and must investigate how various factors affect operations.

\section{Task 1}
Perform an \textbf{LCC analysis} of the crusher, calculating the \textbf{Net Present Value (NPV)}. Include all calculations in your report.

\subsection{Given Data}
\begin{itemize}
    \item \textbf{Discount rate:} 10\%.
    \item \textbf{Calculation period:} 5 years.
    \item \textbf{Operating time:} 8,424 hours per year (24 hours/day, excluding a two-week annual maintenance stop in August).
    \item \textbf{Corrective maintenance:}
    \begin{itemize}
        \item Number of failures per year: 28.
        \item Mean Time to Repair (MTTR): 0.8 days.
        \item Mean Waiting Time for Corrective Maintenance: 0.2 days.
    \end{itemize}
\end{itemize}

\subsection{(a) Availability Calculations}
Calculate and present the following variables in a table:
\begin{itemize}
    \item Preventive maintenance time
    \item Repair time
    \item Corrective maintenance time
    \item Downtime
    \item Available time
    \item Operational availability ($A_o$)
\end{itemize}

\subsection{(b) Life Cycle Cost Calculations}
\begin{itemize}
    \item Calculate annual maintenance cost considering downtime.
    \item Annual revenue: \textbf{265,000 tons/year} at \textbf{100 SEK/ton}.
    \item Include parameters for:
    \begin{itemize}
        \item Performance (initially set to 1, full capacity).
        \item Quality (initially set to 1, 100\% quality yield).
    \end{itemize}
    \item Annual operating costs:
    \begin{itemize}
        \item Energy cost: 600 SEK/hour (scalable with performance).
        \item Operator cost: 500 SEK/hour.
    \end{itemize}
    \item Investment cost: 14,000,000 SEK.
    \item Residual value: Investment reduces by \textbf{50\% per year}.
\end{itemize}

\subsection{(c) Net Present Value (NPV) Calculation}
Calculate present values of annual costs (operation, maintenance, and income) and single amounts (residual value). Then compute NPV using the table format:

\begin{table}[h]
    \centering
    \begin{tabular}{lccc}
        \toprule
        \textbf{Item} & \textbf{Present Value} & \textbf{Annual Amounts} & \textbf{Amount in Year X} \\
        \midrule
        Investment & -XXX &  &  \\
        Maintenance & -XXX & -XXX & -XXX \\
        Operating Cost & -XXX & -XXX & -XXX \\
        Revenue & XXX & XXX &  \\
        Residual Value & XXX & XXX &  \\
        \textbf{NPV} & \textbf{XXX} &  &  \\
        \bottomrule
    \end{tabular}
    \caption{NPV Calculation Summary}
\end{table}

\section{Task 2: Improving Availability}
\subsection{(a) Increasing MTBF}
Perform the same calculations as in Task 1, assuming an additional MTBF. Each \textbf{1\% extra MTBF} increases the investment cost by \textbf{125,000 SEK}. Compute the \textbf{NPV for 10\% extra MTBF} using the same table format.

\textbf{Tip:} A 10\% increase in MTBF is modeled as a \textbf{$1/(1.10)$ reduction} in failure rate.

\subsection{(b) Preventive Maintenance Stops}
Perform the same calculations but include \textbf{preventive maintenance (PM) stops}:
\begin{itemize}
    \item Each PM stop lasts \textbf{24 hours}, costs \textbf{140,000 SEK}, and reduces failures by \textbf{5\%}.
    \item Update failure count, PM time, and maintenance costs.
    \item Compute \textbf{NPV for 6 additional PM stops}.
\end{itemize}

\section{Task 3: Optimization}
\subsection{(a) Finding Optimal MTBF Increase}
Plot \textbf{NPV vs. extra \% MTBF} for the range \textbf{0–100\%}, in \textbf{1\% steps}, using \textbf{6 extra PM stops}.

\subsection{(b) Finding Optimal PM Stops}
Plot \textbf{NPV vs. number of PM stops} in the range \textbf{0–24 stops}, using \textbf{10\% extra MTBF}.

\textbf{Report:} Present the optimal solution with graphs.

\section{Task 4: Sensitivity Analysis}
Perform sensitivity analysis using \textbf{10\% extra MTBF and 6 extra PM stops}.

\subsection{(a) Minimum Quality Yield}
\textbf{Plant efficiency = 95\%.} What is the minimum quality yield needed for a positive NPV?

\subsection{(b) Break-even Price}
\textbf{Plant efficiency = 95\%, Quality = 95\%.} At what crushed stone price does NPV become negative?

\subsection{(c) Interest Rate Sensitivity}
For a \textbf{stone price of 85 SEK}, what discount rate causes NPV $<0$?

\textbf{Report:} Present results and graphs.

\end{document}
